---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(pregnancy.a)
```

# pregnancy.a

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/gipsousp/pregnancy.a/workflows/R-CMD-check/badge.svg)](https://github.com/gipsousp/pregnancy.a/actions)
[![Codecov test coverage](https://codecov.io/gh/gipsousp/pregnancy.a/branch/master/graph/badge.svg)](https://codecov.io/gh/gipsousp/pregnancy.a?branch=master)
[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->

`pregnancy.a` is an R package with the research compendium of the project: expression of the sleep-wake cycle throughout pregnancy: a systematic quantitative literature review. The aim of `pregnancy.a` is to facilitate the research work, in addition to contributing to the reproducibility of the research.

The assemble of this package was inspired by Ben Marwick, Carl Boettiger & Lincoln Mullen article ["Packaging Data Analytical Work Reproducibly Using R (and Friends)"](https://doi.org/10.1080/00031305.2017.1375986).

Learn more about Systematic Quantitative Literature Reviews at <http://bit.ly/2OMxvcD>.

## Installation

`pregnancy.a` is still at the [experimental](https://lifecycle.r-lib.org/articles/stages.html#experimental) stage of development, that means that people can use the package and provide feedback, but it comes with no promises for long term stability.

You can install `pregnancy.a` from GitHub with:

``` {r, eval = FALSE}
# install.packages("pregnancy.a")
devtools::install_github("gipsousp/pregnancy.a", dependencies = TRUE)
```

## Citation

If you use `pregnancy.a` in your research, please consider citing it. We put a lot of work to build and maintain a free and open-source R package. You can find the `pregnancy.a` citation below.

```{r}
citation("pregnancy.a")
```
